---
title: 'Using the party as a shield: additional analyses'
output: 
    bookdown::pdf_document2:
      toc: false
      keep_tex: true
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE)

knitr::read_chunk("data_prep_local.R")
knitr::read_chunk("data_prep.R")
knitr::read_chunk("additional_analysis_R+R.R")
```

```{r set-local-paths, echo=FALSE}

```

```{r read-local-data}

```

```{r parlparsedata}

```


```{r process-local-data}

```

```{r setup-additional-analysis}

```


```{r autoresponse-descriptives}

```


#  Holding Responses and Substantive Response Patterns

We thank the reviewer for raising this concern about the holding responses that we received from MPs, and for raising the question of why we did not follow-up emails which asked about the addresses of correspondents. We have clarified our discussion of holding responses in the paper in a way which we think better addresses the concerns. We now make clearer that the holding responses we received were almost exclusively automated response generated by email out-of-office systems. These automated responses are uniformly sent, so all incoming emails receive a standard message, and are therefore not subject to strategic manipulation. Because of this we are confident that the holding messages are not an indication that our experiment had been discovered by some MPs. 

The reviewer asks why did we not follow-up these holding responses with a re-statement of the correspondents address. This was in part because holding emails did not request this. The purpose of holding emails was generally to acknowledge receipt, but they also often contained other material, frequently letting those who write to MPs know that it may take some time to receive a response. Because of the convention that MPs deal with personal inquiries only from their own constituents, one of the frequent pieces of information in these holding emails was to check that letters included correspondents names and addresses. This was generally directed at any correspondents who had not provided an address in constituency in their original letter, rather than as a request for the information to be provided again from correspondents who had included that information already. 

The frequency with which MPs followed up on holding responses to provide substantive responses gives further reassurance that MPs holding responses do not signal reluctance to engage with the letters we arranged to be sent to MP. Holding responses were generally a prelude to a further more substantive response. In fact `r round(prop_holding_to_substantive*100)` percent of holding responses were followed up with a substantive response. By comparison, `r round(prop_noholding_to_substantive*100)` percent of letters where no holding response was sent received a substantive response. (We also note that Reviewer 1 states that more than half responses are holding responses but in fact we have more substantive responses that holding responses: we sent `r nrow(main)` letters, there are `r sum(main$autoresponse_exists)` holding responses, whilst there are  `r sum(main$manualresponse_exists_inc_post_count_nonresponse)` substantive responses.) 



# Exploratory Analysis of MP Responsiveness{#explore-response}

```{r descriptive-responsiveness-analysis-setup}

```


```{r descriptive-response-analysis}

```

```{r descriptive-response-results-plot, fig.cap="Coefficient plot of linear probability model using largely categorical independent variables, where the dependent variable is whether the letter has a response by either email or post (1) or no recorded response by either email or post (0). The plot includes coeffiecients from models with each potential dependent variable entered separately, and a full model with all potential dependent variables entered together. All models include MP random effects."}

```


```{r descriptive-response-analysis-cont}

```

```{r descriptive-response-results-cont-plot, fig.cap="Coefficient plot of linear probability model using some continuous categorical variables, where the dependent variable is whether the letter has a response by either email or post (1) or no recorded response by either email or post (0). The plot includes coeffiecients from models with each potential dependent variable entered separately, and a full model with all potential dependent variables entered together. All models include MP random effects.", eval=FALSE}

```

<!-- Reviewer 4 says that it might be fun/interesting to examine whether response rate to letters to MPs are associated with things like: MP gender, MP seniority, marginaltiy, est. Brexit Referendum Vote, Party, length of MP service, MP seniority (backbench v frontbench MPs) -->

<!-- We have some data which could be used to answer some of these questions from the BES data (party, gender, marginality, Brexit Referendum vote), it would be good to supplement this with the data on length of MP service, MP frontbench v backbench. -->

<!-- We could examine the association between whether the MP responds or not to our letter in a model with MP random effects. For some variables we have to decide whether to use either use categorical or continuous versions of those variables (e.g. to make identification of the constituencies involved harder - but see discussion below).  -->


<!-- The results of some preliminary analysis using categorical versions of variables is shown in Figure \@ref(fig:descriptive-response-results-plot) and a similar analysis using continuous versions of the variables is shown in Figure \@ref(fig:descriptive-response-results-cont-plot). In both cases the results suggest that there is not much relationship between MP response rates and either constituency marginality or with the party of the MP, but that there is an association between response rates and the level of support for leave in the EU referendum. -->

To help understand our null results we provide a exploratory and speculative analysis of how response rates vary across MPs and constituencies, examining whether response rates are associated with MP and constituency characteristics. One relevant question is whether cross-constituency MP responsiveness varies in ways which might be expected given an assumption that responsiveness varies according to strategic considerations. We examine the following MP characteristics: 

*  MP party: comparing Conservative Party MP as the base line to all other parties MPs (BES constituency file).
*  MP gender: with female MPs as the baseline category (BES constituency file).
*  MP seniority: comparing frontbench MPs to backbench MPs as the baseline category. We use parlparse data to identify MP who held Ministerial or Shadow Ministerial positions at any point during the period of our study.
*  MP length of service: number of decades MP has served in the House of Commons. We use parlparse data to identify the number of decades of service given by MPs who represented a constituency to the outset of our study.

We also examine the following constituency characteristics:

*  Winning party majority in 2017 General Election, with four categories where the majority is: above 10% (baseline), 5-10%, 2-5% and below 2% (BES constituency file).
*  Estimated 2016 referendum vote in the constituency (Hanretty estimates from the BES constituency file).


<!-- For example we could use a binary version of the party variable: e.g. Conservative v all other parties, use `cut_number` to create categories of the estimated Brexit vote in the constituency. We could also use use a categorical measure of marginality (following the discussion of marginality in the [House of Commons Library insight on paper on marginality](https://commonslibrary.parliament.uk/2024-general-election-marginality/) we could consider constituencies where the result was not very close alongside three categories of marginal, where the winning margin was less than 10%, where the winning margin was less than 5% and where the winning margin was less than 2%).    -->

We examine the association between MP responsiveness and these variables using a linear probability model with MP random effects. We run models where each independent variable is entered separately, and a full model where all the independent variable are entered together. The results of these models are shown in Figure \@ref(fig:descriptive-response-results-plot). 

We find mixed evidence on the question of whether strategic considerations drive MP responsiveness. We find some patterns which could suggest that differential responsiveness might be partly explained by variation in the importance of valence considerations. We find that MP responsiveness was significantly related to length of service, which may be because more newer MPs have more need to build a local reputation, with more established MPs having had more opportunity to already develop that. We also find that MP responsiveness was significantly higher among MP representing seats with the lowest estimated support for leaving the European Union in the 2016 referendum, which could potentially be because it is more important for MPs to establish their activity and competence in constituencies where national minority positions are in the majority. However, we do not find a clear association between the marginality of the results in the 2017 General Election and the MP responsiveness, none of the categories of marginal seat shows an significantly higher response rate than found in MPs in safe seats (the baseline category). Given that electoral incentives are more pronounced in more marginal seats, this provides some evidence against the idea that strategic electoral considerations play the major role in determining MP responsiveness to policy inquiries from constituents. We also did not find a relationship between party, gender or frontbench/backbench MPs and probability of an MP responding to a letter. 



<!-- Many of our letters were about Brexit related issues, and we sent them in a period where parties had less yet to form a sufficiently clear policy on these issues.  -->



<!--  However, we think that a lack of a party line would actually give MPs more room for manoeuvre to selectively blame their party for positions unpopular with a constituent. Furthermore, we were able to identify reasonably clear party leadership stances on the issues upon which constituents sent letters to MPs in the study.    -->


<!-- and a similar analysis using continuous versions of the variables is shown in Figure \@ref(fig:descriptive-response-results-cont-plot).  -->


## Sharing the data for analysis has a high risk of revealing which MPs respond to letters

```{r cases-per-cell-experiment}

```

```{r cases-per-cell-response-experiment}

```

Sharing the data on which the descriptive analysis is based on will deanonymise the response rate information (so people will be able to tell from our data whether particularly MPs responded to the emails we sent them). I think the options available to us are:

  1.  Undertake the analysis but withhold the data and code for this part of the analysis.
  1.  Undertake the analysis and provide replication data and code, on the basis that we think it is acceptable to deanonymise MP response rates.
  1.  Find another option I haven't thought of in the analysis, or in the approach to sharing the data which does not deanonymise the MPs.
  1.  Not undertake this part of the analysis.

I think that my preference is for option 1.

Some further detail on these questions is provided below:

I think we risk deanonymising out data if we with cells to be smaller than about five, and we are very likely to have many cells much smaller than this level. 

From the data we share for the balance analysis it is possible to figure out which constituencies are in our experiment and which constituencies are not in our experiment. I think we agreed that this is acceptable because it reveals information only about our behaviour and not about the individual MPs behaviour. 

It is quite tricky to avoid revealing information about individual MPs responses rates in our exploratory non-response analysis. If we use continuous measures for constituency level variables, then when we share this then just one variable by itself will generally be sufficient to identify the constituency. Categorisation can address that issues with respect to single variables. However, even with very broad categorisation of the data across a three variables the data will effectively allow the users to identify which constituencies particularly when combined with the information about which constituencies are in our experiment. 

For example, as show in Table \ref{tab:cases-per-cell-experiment} even if we create two party categories (Con v All others), three Brexit estimated leave vote categories, and two marginality categories (above/below 10% majority) there are many constituencies that are completely identified (cell size of 1), and most of the cells have fewer than 5 cases.

Separately releasing datasets for each category does not resolve this issue. As shown in Table \ref{tab:cases-per-cell-response-experiment}, just providing the information on response patterns will enable many constituencies to be deterministically linked across the datasets (without even considering the use of the information from the categorisations to supplement this). 

Hence, I don't currently see a way to release information for the descriptive analysis of response rates by constituency and MP characteristics without revealing information about the responsiveness of particular MPs.




