---
title: 'Using the party as a shield: Power analysis'
author: "Daniel Bishof, Vanessa Cheng-Matuno, Gidon Cohen, Sarah Cohen, Florian Foos,
  Patrick M Kuhn, Kyriaki Nanou, Neil Visalvanich, Nick Vivyan"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex # Use xelatex for better font support
    pandoc_arg: --listings
    includes:
        in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE)

knitr::read_chunk("power_analysis.R")
```

The power analysis was conducted at the end of the project (but based on code implemented at two earlier phases in the project - most recently from the first recruitment phase to inform decisions about future steps). Note, that MP non-response is not considered and this will have a major impact on power. 

We shared the full code for our power analysis with the working paper and it can be accessed online on OSF.

\paragraph{Theory and Data Generating Mechanism \label{app:power}}

Letter $i$ is sent to MP $\alpha_{\mathrm{mp}\left[i\right]}$, from constituents who agree with and disagree with the MP on an issue. Where:

\begin{itemize}
    \item Binary $DV_i$ = e.g. Probability that MP responds to letter $i$
    \item Continuous $DV_i$ = e.g. log-ratio of MP v party mentions in response to letter $i$  
    \item $IV_i$ = MPs Party agrees with a constituent on Issue Position Expressed in Letter $i$
    \item $\alpha_{\mathrm{mp}\left[i\right]}$  = MP fixed effect (for MP to whom letter $i$ is sent), representing e.g. differential responsiveness across MPs.
\end{itemize}

We assume a linear data-generating mechanism:\\
$$DV_i = \beta_1 \cdot IV_i + \alpha_{\mathrm{mp}\left[i\right]}  + \epsilon_i $$

With correlated MP effects, where we send letters on all the MPs on all the issues we have.  

Figures \@ref(fig:contin-plot) and \@ref(fig:binary-plot) report the power of our design across ATEs.   It becomes evident that we are well powered (>.8) for ATEs around 0.1 for the binary and ATEs of 0.05 for continuous outcomes. In comparison to previous audit studies, we are well powered particularly given that we relied on `actual' voters. 

```{r power-anal-setup}

```

```{r power-anal-functions}

```

```{r set-n-sims-long}

```

```{r run-power-anal}

```

```{r contin-plot, fig.cap="Power for continuous outcomes."}

```

```{r binary-plot, fig.cap="Power for binary outcomes."}

```

